---
title: "1_SiteComparisonEnvironmental"
author: "Sara Devi Swaminathan"
date: "`r Sys.Date()`"
output: html_document
toc: true
toc_float: true
number_sections: true
---
# Table of Contents {#table-of-contents}

## Setup: working directory and packages

Load libraries and set working directory

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(zoo)
library(parallel)
library(brms)
library(reshape2)
library(bayestestR)
```

## Read in data and filter sites and partial days

```{r}
# Load data frame
YSIdata19 <- read.csv("data/sonde_data_withSeptNurseryMinidot.csv") %>%
  dplyr::select(site, date, time, Depth, DOmgL, Sal_PSU, pH, Temp_degC, CHL_uGL, Turb_FNU, TDS_mgL) %>% #select columns we use
  mutate(date = as.Date(date, format = '%m/%d/%y')) %>% # reformat date
  filter(site %in% c("munson", "nursery"))%>%
  mutate(site = factor(site, levels = c("nursery", "munson"))) %>%
  mutate(DT = as.POSIXct(paste(date, time), format = "%Y-%m-%d %H:%M:%S")) %>% # make DateTime column
  mutate(fulldays = factor(ifelse(date >= "2019-06-12" & date <= "2019-07-07", "JJ",
                       ifelse(date >= "2019-07-10" & date <= "2019-08-04", "JA",
                          ifelse(date >= "2019-08-07" & date <= "2019-09-08", "AS",
                                  ifelse(date >= "2019-09-10" & date <= "2019-10-07", "SO", NA)))))) %>% #mark full days with deployment months, NA for partial days
  mutate(fulldays = factor(fulldays, levels = c("JJ", "JA", "AS", "SO"))) %>%
  arrange(site, DT)

#filter to only sites where corals were collected for this experiment
YSIfiltered <- YSIdata19 %>%
  filter(site %in% c("munson", "nursery"))%>%
  filter(!is.na(fulldays)) %>%
  group_by(site) %>%
  arrange(site, DT)

```

# calculate rolling averages of DO, Turbidity, TDS, pH, and Salinity

```{r}
YSI_ma <- YSIfiltered %>%
  dplyr::group_by(site) %>%
  dplyr::arrange(DT, .by_group = TRUE) %>% #arrange by datetime and group by site
  mutate(maTemp_24 = rollmean(Temp_degC, k = 144, fill = NA),  # 24-hr temp running average (24 hrs * 60 min = 1440. Divided by measurements every 10 minutes.)
    maDO_24 = rollmean(DOmgL, k = 144, fill = NA),  # 24-hr DO running average
    maTurb_24 = rollmean(Turb_FNU, k = 144, fill = NA),
    maTDS_24 = rollmean(TDS_mgL, k = 144, fill = NA),
    mapH_24 = rollmean(pH, k = 144, fill = NA),
    maSal_24 = rollmean(Sal_PSU, k = 144, fill = NA))

# filter to munson (inshore) alone
ma_munson <- YSI_ma %>%
  filter(site == "munson") 

# filter to nursery (offshore) alone
ma_nursery <- YSI_ma %>%
  filter(site == "nursery")

# summarize moving average df with mins and max values
ysiSumm <- YSI_ma %>%
  group_by(site, date)%>%
  mutate(DOmax = max(DOmgL), 
            DOmin = min(DOmgL), 
            DOmean = mean(DOmgL), 
            tempMax = max(Temp_degC), 
            tempMin = min(Temp_degC), 
            tempMean = mean(Temp_degC), 
            Turbmax = max(Turb_FNU), 
            Turbmin = min(Turb_FNU), 
            Turbmean = mean(Turb_FNU), 
            pHmax = max(pH),
            pHmin = min(pH),
            pHmean = mean(pH), 
            Sal_PSUmax = max(Sal_PSU),
            Sal_PSUmin = min(Sal_PSU),
            Sal_PSUmean = mean(Sal_PSU),
            TDSMax = max(TDS_mgL), 
            TDSMin = min(TDS_mgL), 
            TDSMean = mean(TDS_mgL))

# find all instances of DO less than 4mg/L
lowDO<-YSI_ma%>%
  filter(DOmgL<4)

# subset to temp data
YSI_ma_temp<- YSI_ma %>%
  mutate(datetime_index = as.numeric(DT))%>%
  dplyr::select(Temp_degC, site, DT, datetime_index, maTemp_24)%>%
  unique()%>%
  group_by(datetime_index, site)%>%
  summarise(Temp_degC = mean(Temp_degC))%>%
  mutate(logTemp = log(Temp_degC))

# subset to DO data
YSI_ma_do<- YSI_ma %>%
  mutate(datetime_index = as.numeric(DT))%>%
  dplyr::select(DOmgL, site, DT, datetime_index, maDO_24)%>%
  unique()%>%
  group_by(datetime_index, site)%>%
  summarise(DOmgL = mean(DOmgL))
```

# set plotting colors 
```{r}
siteColorsPoint = c("munson" = "#f4a582", "nursery" = "#abd9e9")
siteColorsLine = c("munson" = "#d7191c", "nursery" = "#2c7bb6")
```

## calculate days Munson average temp > 31 deg (50days)
```{r}
ma_munson%>%
  ungroup()%>%
  dplyr::group_by(date)%>%
  summarise(dailyMean = mean(maTemp_24))%>%
  filter(dailyMean > 31)

ma_munson%>%
  summarise(mean = mean(Temp_degC))
```

## calculate days Nursery average > 31 deg (14)
```{r}
ma_nursery%>%
  group_by(date)%>%
  summarise(dailyMean = mean(maTemp_24))%>%
  filter(dailyMean > 31)

ma_nursery%>%
  summarise(mean = mean(Temp_degC))
```

## calculate mean diel fluctuation at each site
```{r}
YSI_ma %>%
  select(date, site, Temp_degC)%>%
  group_by(date, site)%>%
  summarise(min = min(Temp_degC), 
         max = max(Temp_degC),
         diel = max - min)%>%
  ungroup()%>%
  group_by(site)%>%
  summarise(meanDiel = mean(diel))
```

# Temperature plot

## with points
```{r}
# Plot 24-running average over raw
bothSitesTempplot <- ggplot(data = YSI_ma, aes(x = DT)) +
  geom_point(aes(y = Temp_degC, fill = site), size = 1, shape = 21, alpha = 0.3, stroke = 0) +
  scale_color_manual(values=siteColorsLine) + # Manually change colors of plotted data
  scale_fill_manual(values=siteColorsPoint) + # Manually change colors of plotted data
  geom_line(aes (y = maTemp_24, color = site), size = 1) +
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom") + 
  labs(color = "") +
  labs(title = "Summer 2019 temperatures at inshore and offshore sites",  
       #subtitle = "2019",
       x = "\nDate", # \n makes space above and below
       y = "Temp (\u00B0C)\n") +
  scale_y_continuous(#expand = c(0,0),   # # Sets the 0 of the y-axis to start at the plot outline and not have it floating above the plot
    limits = c(27.5,33),  # Sets the y-axis to range from 3 to 9.5, based on the site with the widest range
    breaks = seq(27.5,33,1)) +  # Defines breaks in a sequence from 3 to 9.5 by increments of 1
  scale_x_datetime(breaks = as.POSIXct(c("2019-06-12", "2019-07-01", "2019-08-01", "2019-09-01", "2019-10-01")),
                   labels = c("12 Jun", "1 Jul", "1 Aug", "1 Sep", "1 Oct")) +
  theme(axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10))
# minor_breaks = as.POSIXct(c("2019-06-01", "2019-07-01", "2019-08-01", "2019-09-01", "2019-10-01")) 
bothSitesTempplot # Print plot

### save plot with specified parameters directly to a specific file path
ggsave(file = "fig/TempbothSites2019.pdf", plot = bothSitesTempplot, width = 8, height = 6)
ggsave(file = "fig/TempbothSites2019.svg", plot = bothSitesTempplot, width = 8, height = 6)
```

## with geom ribbon

```{r}
# Plot 24-running average over raw
(bothSitesTemp_simp <- ggplot(data = ysiSumm, aes(x = DT, color = site, fill = site)) +
  geom_ribbon(aes(ymin = tempMin, ymax = tempMax, alpha = 0.5), color = NA)+
  geom_line(aes (y = maTemp_24, color = site), size = 1) + 
  scale_color_manual(values=siteColorsLine) + # Manually change colors of plotted data
  scale_fill_manual(values=siteColorsPoint) + # Manually change colors of plotted data
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom") + 
  labs(color = "") +
  labs(x = "\nDate", # \n makes space above and below
       y = "Temp (\u00B0C)\n") +
  scale_y_continuous(#expand = c(0,0),   # # Sets the 0 of the y-axis to start at the plot outline and not have it floating above the plot
    limits = c(27.5,33),  # Sets the y-axis to range from 3 to 9.5, based on the site with the widest range
    breaks = seq(27.5,33,1)) +  # Defines breaks in a sequence from 27.5 to 33 by increments of 1
  scale_x_datetime(breaks = as.POSIXct(c("2019-07-01", "2019-08-01", "2019-09-01", "2019-10-01")),
                   labels = c( "1 Jul 2019", "1 Aug 2019", "1 Sep 2019", "1 Oct 2019")) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15)) + 
  theme(text=element_text(size=15)) + 
  theme(legend.position="none"))
 
bothSitesTemp_simp # Print plot

### save plot with specified parameters directly to a specific file path
ggsave(file = "fig/bothSitesTemp_simp.svg", plot = bothSitesTemp_simp, width = 8, height = 6)

ggsave(file = "fig/bothSitesTemp_simp.pdf", plot = bothSitesTemp_simp, width = 8, height = 6)
```

# DO plot
## with points

```{r}
# Plot 24-running average over raw
bothSitesDOplot <- ggplot(data = YSI_ma, aes(x = DT)) +
  geom_point(aes(y = DOmgL, fill = site), size = 1, shape = 21, alpha = 0.3, stroke = 0) +
  geom_line(aes (y = maDO_24, color = site), size = 1) + 
  scale_color_manual(values=siteColorsLine) + # Manually change colors of plotted data
  scale_fill_manual(values=siteColorsPoint) + # Manually change colors of plotted data
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom") + 
  labs(color = "") +
  labs(title = "Site DO differences",  
       #subtitle = "2019",
       x = "\nDate", # \n makes space above and below
       y = "DO mg/L") +
  scale_y_continuous(#expand = c(0,0),   # # Sets the 0 of the y-axis to start at the plot outline and not have it floating above the plot
    limits = c(3,8),  # Sets the y-axis to range from 3 to 9.5, based on the site with the widest range
    breaks = seq(3,8,1)) +  # Defines breaks in a sequence from 3 to 9.5 by increments of 1
  scale_x_datetime(breaks = as.POSIXct(c("2019-06-12", "2019-07-01", "2019-08-01", "2019-09-01", "2019-10-01")),
                   labels = c("12 Jun", "1 Jul", "1 Aug", "1 Sep", "1 Oct")) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15)) + 
  theme(text=element_text(size=15)) + 
  theme(legend.position="none")
  
bothSitesDOplot # Print plot

### save plot with specified parameters directly to a specific file path
ggsave(file = "fig/DObothSites_bothSegments.pdf", plot = bothSitesDOplot, width = 8, height = 6)
ggsave(file = "fig/DObothSites_bothSegments.svg", plot = bothSitesDOplot, width = 8, height = 6)
```

## with geom ribbon

```{r}
# Plot 24-running average over raw
(bothSitesDO_simp <- ggplot(data = ysiSumm, aes(x = DT, color = site, fill = site))+
  geom_ribbon(aes(ymin = DOmin, ymax = DOmax, alpha = 0.5), color = NA)+
  geom_line(aes (y = maDO_24, color = site), size = 1) + 
  scale_color_manual(values=siteColorsLine) + # Manually change colors of plotted data
  scale_fill_manual(values=siteColorsPoint) + # Manually change colors of plotted data
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom") + 
  labs(color = "") +
  labs(x = "\nDate", # \n makes space above and below
       y = "DO (mg/L)") +
  scale_y_continuous(#expand = c(0,0),   # # Sets the 0 of the y-axis to start at the plot outline and not have it floating above the plot
    limits = c(0,8),  # Sets the y-axis to range from 3 to 9.5, based on the site with the widest range
    breaks = seq(0,8,2)) +  # Defines breaks in a sequence from 3 to 9.5 by increments of 1
  scale_x_datetime(breaks = as.POSIXct(c("2019-07-01", "2019-08-01", "2019-09-01", "2019-10-01")),
                   labels = c( "1 Jul 2019", "1 Aug 2019", "1 Sep 2019", "1 Oct 2019")) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15)) + 
  theme(text=element_text(size=15)) + 
  theme(legend.position="none"))
 
bothSitesDO_simp # Print plot

### save plot with specified parameters directly to a specific file path
ggsave(file = "fig/bothSitesDO_simp.svg", plot = bothSitesDO_simp, width = 8, height = 6)
ggsave(file = "fig/bothSitesDO_simp.pdf", plot = bothSitesDO_simp, width = 8, height = 6)
``` 

# Bayesian models of environmental data

## First, set instructions for sampler

```{r}
n_cores <- detectCores() # this will determine how many cores your computer has so that it can use all of its processing power
n_chains <- 2 
n_iter <- 4000
n_warmup <- 2000
```

# temperature models - temp_brm5 is the best model

```{r}
hist(YSI_ma$maTemp_24) # visualize data
hist(log(YSI_ma$maTemp_24)) # visualize data
########################################################################################################################################

#define model
temp_mod1 <- bf(Temp_degC ~  site + s(datetime_index,by = site, m = 1, k=5), 
                family =  gaussian())

##### Get priors
get_prior(temp_mod1, data = YSI_ma_temp) 
 
temp_prior<- c(prior(normal(0, 5), class = "Intercept"),
            prior(normal(0, 2), class = "b"))

                          
# temp_brm1 <- brm(temp_mod1,
#                data = YSI_ma_temp,
#                prior = temp_prior,
#                cores = n_cores,
#                chains = n_chains,
#               # init = "0",
#                iter = n_iter,
#                warmup = n_warmup)

# pp_check(temp_brm1, ndraws = 100)
# pp_check(temp_brm1,type = "loo_pit_overlay", ndraws = 100)
# bayes_R2(temp_brm1) #0.83
# temp_brm1

# ###########################################################################################################################################
### tried a log transform, but no improvement

# 
# #define model
# temp_mod2 <- bf(logTemp ~  site + s(datetime_index, by = site,m=1,  k=5),
#                 family =  gaussian())
# 
# ##### Get priors
# get_prior(temp_mod2, data = data_new)
# 
# # temp_prior <- c(prior(normal(3.1, 1), class = "Intercept"),
# #                 prior(normal(0, 1), class = "b"))
# 
# temp_prior<- c(prior(normal(0, 5), class = "Intercept"),
#             prior(normal(0, 2), class = "b"))
# 
# 
# temp_brm2 <- brm(temp_mod2,
#                data = YSI_ma_temp,
#                prior = temp_prior,
#                cores = n_cores,
#                chains = n_chains,
#               # init = "0",
#                iter = n_iter,
#                warmup = n_warmup)
# 
#  pp_check(temp_brm2, ndraws = 100)
# pp_check(temp_brm2,type = "loo_pit_overlay", ndraws = 100)
# bayes_R2(temp_brm2) #0.78

# ###########################################################################################################################################
# trying as a mixture model - did not converge at all
##### Set priors

# #define model
# temp_mod3 <- bf(Temp_degC ~  site + s(datetime_index,by = site, m = 1, k=5), 
#                 family =  mixture(gaussian, gaussian))
# 
# ##### Get priors
# get_prior(temp_mod3, data = YSI_ma_temp) 
#  
# 
# temp_prior<- c(prior(normal(29, 5), class = "Intercept", dpar = mu1),
#                 prior(normal(31, 5), class = "Intercept", dpar = mu2))
#            # prior(normal(0, 2), class = "sd"),
#             # prior(normal(0, 2), class = "b"))
# 
#                           
# temp_brm3 <- brm(temp_mod3,
#                data = YSI_ma_temp,
#                prior = temp_prior,
#                cores = n_cores,
#                chains = n_chains,
#               init = "0",
#                iter = n_iter,
#                warmup = n_warmup)
# 
# pp_check(temp_brm3, ndraws = 100)
# pp_check(temp_brm3,type = "loo_pit_overlay", ndraws = 100)
# bayes_R2(temp_brm3)

# ###########################################################################################################################################

#define model
temp_mod4 <- bf(Temp_degC ~  site + s(datetime_index, bs = "cr", k=20), 
                family =  gaussian())

##### Get priors
get_prior(temp_mod1, data = YSI_ma_temp) 
                          
# temp_brm4 <- brm(temp_mod4,
#                data = YSI_ma_temp,
#                prior = temp_prior,
#                cores = n_cores,
#                chains = n_chains,
#               init = "0",
#                iter = n_iter,
#                warmup = n_warmup)
# 
# pp_check(temp_brm4, ndraws = 100)
# pp_check(temp_brm4,type = "loo_pit_overlay", ndraws = 100)
# bayes_R2(temp_brm4) #0.89
# temp_brm4
# model_weights(temp_brm1, temp_brm4)# 4 is better
# ###########################################################################################################################################

#define model
temp_mod5 <- bf(Temp_degC ~  site + s(datetime_index, bs = "cr", k=30), 
                family =  gaussian())
                          
temp_brm5 <- brm(temp_mod5,
               data = YSI_ma_temp,
               prior = temp_prior,
               cores = n_cores,
               chains = n_chains,
              init = "0",
               iter = n_iter,
               warmup = n_warmup)
saveRDS(temp_brm5, "model outputs/temp_brm.rds")
temp_brm5 <- readRDS("model outputs/temp_brm.rds")

pp_check(temp_brm5, ndraws = 100)
#pp_check(temp_brm4, ndraws = 100)
pp_check(temp_brm5,type = "loo_pit_overlay", ndraws = 100)
bayes_R2(temp_brm5) #0.91
temp_brm5
#model_weights(temp_brm5, temp_brm4)# 5 is better

############################################################################################################################################

#define model
temp_mod6 <- bf(Temp_degC ~  site + s(datetime_index, bs = "cr", k=50), 
                family =  gaussian())
                          
# temp_brm6 <- brm(temp_mod5,
#                data = YSI_ma_temp,
#                prior = temp_prior,
#                cores = n_cores,
#                chains = n_chains,
#               init = "0",
#                iter = n_iter,
#                warmup = n_warmup)
# 
# pp_check(temp_brm6, ndraws = 100)
# pp_check(temp_brm5, ndraws = 100)
# pp_check(temp_brm6,type = "loo_pit_overlay", ndraws = 100)
# bayes_R2(temp_brm6) #0.91
# temp_brm6
# model_weights(temp_brm5, temp_brm6)# 5 is  better

############################################################################################################################################
#define model
temp_mod7 <- bf(Temp_degC ~  site + s(datetime_index, by = site, id = 1, k=30) , 
                family =  gaussian())

# temp_brm7 <- brm(temp_mod7,
#                data = YSI_ma_temp,
#                prior = temp_prior,
#                cores = n_cores,
#                chains = n_chains,
#               init = "0",
#                iter = n_iter,
#                warmup = n_warmup)
# 
# pp_check(temp_brm7, ndraws = 100)
# pp_check(temp_brm5, ndraws = 100)
# pp_check(temp_brm7,type = "loo_pit_overlay", ndraws = 100)
# bayes_R2(temp_brm5) #0.91
# temp_brm5
# model_weights(temp_brm5, temp_brm7)# 5 is better
############################################################################################################################################
# get credible intervals of best model
#-Get posterior draws for all parameter estimates-#
posterior_draws_temp <- temp_brm5 %>%
 posterior_samples() %>%
  melt()%>%
  as_tibble() %>%
  dplyr::select(contains(c('Temp_degC')))

describe_posterior(temp_brm5, ci = 0.95)
bayes_R2(temp_brm5)
```

# DO models - do_brm6 is the best model

```{r}
hist(YSI_ma$maDO_24)
hist(log(YSI_ma$maDO_24))
###########################################################################################################################################
##### Set priors
#define model
do_mod1 <- bf(DOmgL ~  site + s(datetime_index,by = site, m = 1, k=5), 
                family =  gaussian())

##### Get priors
get_prior(do_mod1, data = YSI_ma_do) 

YSI_ma_do%>%
  group_by(site)%>%
  summarise(meanDO = mean(DOmgL))

do_prior<- c(prior(normal(6, 1), class = "Intercept"),
            prior(normal(0, 2), class = "b"))

                          
# do_brm1 <- brm(do_mod1,
#                data = YSI_ma_do,
#                prior = do_prior,
#                cores = n_cores,
#                chains = n_chains,
#               # init = "0",
#                iter = n_iter,
#                warmup = n_warmup)
# 
# pp_check(do_brm1, ndraws = 100)
# pp_check(do_brm1,type = "loo_pit_overlay", ndraws = 100)
# bayes_R2(do_brm1) #0.13
# do_brm1
############################################################################################################################################

#define model
do_mod2 <- bf(DOmgL ~  site + s(datetime_index, bs = "cr", k=20), 
                family =  gaussian())
                          
# do_brm2 <- brm(do_mod2,
#                data = YSI_ma_do,
#                prior = do_prior,
#                cores = n_cores,
#                chains = n_chains,
#               init = "0",
#                iter = n_iter,
#                warmup = n_warmup)
# 
# pp_check(do_brm2, ndraws = 100)
# pp_check(do_brm2,type = "loo_pit_overlay", ndraws = 100)
# bayes_R2(do_brm2) #0.23
# do_brm2
# model_weights(do_brm1, do_brm2)
# 
# saveRDS(do_brm2, "model outputs/DO_brm.rds")
############################################################################################################################################
#define model
do_mod3 <- bf(DOmgL ~  site + s(datetime_index, bs = "cr", k=30), 
                family =  gaussian())
                          
# do_brm3 <- brm(do_mod3,
#                data = YSI_ma_do,
#                prior = do_prior,
#                cores = n_cores,
#                chains = n_chains,
#               init = "0",
#                iter = n_iter,
#                warmup = n_warmup)
# 
# pp_check(do_brm3, ndraws = 100)
# pp_check(do_brm2, ndraws = 100)
# pp_check(do_brm3,type = "loo_pit_overlay", ndraws = 100)
# bayes_R2(do_brm3) #0.24
# do_brm3
# model_weights(do_brm3, do_brm2)# 3 is better
############################################################################################################################################
#define model
do_mod4 <- bf(DOmgL ~  site + s(datetime_index, bs = "cr", k=40), 
                family =  gaussian())
                          
# do_brm4 <- brm(do_mod4,
#                data = YSI_ma_do,
#                prior = do_prior,
#                cores = n_cores,
#                chains = n_chains,
#               init = "0",
#                iter = n_iter,
#                warmup = n_warmup)
# 
# pp_check(do_brm4, ndraws = 100)
# pp_check(do_brm3, ndraws = 100)
# pp_check(do_brm4,type = "loo_pit_overlay", ndraws = 100)
# bayes_R2(do_brm4) #0.26
# do_brm4
# model_weights(do_brm3, do_brm4)# 4 is better
############################################################################################################################################
#define model
do_mod5 <- bf(DOmgL ~  site + s(datetime_index, bs = "cr", k=50), 
                family =  gaussian())

# do_brm5 <- brm(do_mod5,
#                data = YSI_ma_do,
#                prior = do_prior,
#                cores = n_cores,
#                chains = n_chains,
#               init = "0",
#                iter = n_iter,
#                warmup = n_warmup)
# 
# pp_check(do_brm5, ndraws = 100)
# pp_check(do_brm4, ndraws = 100)
# pp_check(do_brm5,type = "loo_pit_overlay", ndraws = 100)
# bayes_R2(do_brm5) #0.27
# do_brm5
# model_weights(do_brm5, do_brm4)# 5 is better
#############################################################################################################################
#define model
do_mod6 <- bf(DOmgL ~  site + s(datetime_index, bs = "cr", k=100), 
                family =  gaussian())

do_brm6 <- brm(do_mod6,
               data = YSI_ma_do,
               prior = do_prior,
               cores = n_cores,
               chains = n_chains,
              init = "0",
               iter = n_iter,
               warmup = n_warmup)

saveRDS(do_brm6, "model outputs/DO_brm.rds")
do_brm6 <- readRDS("model outputs/DO_brm.rds")
#pp_check(do_brm5, ndraws = 100)
pp_check(do_brm6, ndraws = 100)
pp_check(do_brm6,type = "loo_pit_overlay", ndraws = 100)
bayes_R2(do_brm6) #0.23
do_brm6
#model_weights(do_brm5, do_brm6)# 6 is better


#############################################################################################################################
#define model
do_mod7 <- bf(DOmgL ~  site , 
                family =  gaussian())

# do_brm7 <- brm(do_mod7,
#                data = YSI_ma_do,
#                prior = do_prior,
#                cores = n_cores,
#                chains = n_chains,
#               #init = "0",
#                iter = n_iter,
#                warmup = n_warmup)
# 
# pp_check(do_brm7, ndraws = 100)
# pp_check(do_brm6, ndraws = 100)
# pp_check(do_brm7,type = "loo_pit_overlay", ndraws = 100)
# bayes_R2(do_brm7) #0.29
# do_brm7
# model_weights(do_brm7, do_brm6)# with site is better
#############################################################################################################################

# get credible intervals of best model
#-Get posterior draws for all parameter estimates-#
posterior_draws_do <- do_brm6 %>%
 posterior_samples() %>%
  melt()%>%
  as_tibble() %>%
  dplyr::select(contains(c('DOmgL')))

describe_posterior(do_brm6, ci = 0.95)
bayes_R2(do_brm6)
############################################################################################################################################
```


# Turbidity, pH, Salinity, and and TDS plots

```{r}

ysiSumm%>%
  group_by(site)%>%
  na.omit()%>%
  summarize(meanSal = mean(maSal_24))

ysiSumm%>%
  group_by(site)%>%
  na.omit()%>%
  summarize(meanTDS = mean(maTDS_24))

ysiSumm%>%
  group_by(site)%>%
  na.omit()%>%
  summarize(meanTurb = mean(maTurb_24))

ysiSumm%>%
  group_by(site)%>%
  na.omit()%>%
  summarize(meanpH = mean(mapH_24))


# Plot 24-running average TURBIDITY over raw
(bothSitesTurb_simp <- ggplot(data = ysiSumm, aes(x = DT, color = site, fill = site)) +
  geom_ribbon(aes(ymin = Turbmin, ymax = Turbmax, alpha = 0.5), color = NA)+
  geom_line(aes (y = maTurb_24, color = site), size = 1) + 
  scale_color_manual(values=siteColorsLine) + # Manually change colors of plotted data
  scale_fill_manual(values=siteColorsPoint) + # Manually change colors of plotted data
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom") + 
  labs(color = "") +
  labs(x = "\nDate", # \n makes space above and below
       y = "Turbidity") +
scale_y_continuous(expand = c(0,0),   # # Sets the 0 of the y-axis to start at the plot outline and not have it floating above the plot
    limits = c(-2,10))+  # Sets the y-axis to range from 0 to 10, based on the site with the widest range
 #   breaks = seq(0,10,1)) +  # Defines breaks in a sequence from 27.5 to 33 by increments of 1
  scale_x_datetime(breaks = as.POSIXct(c("2019-07-01", "2019-08-01", "2019-09-01", "2019-10-01")),
                   labels = c( "1-Jul", "1-Aug", "1-Sep", "1-Oct")) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15)) + 
  theme(text=element_text(size=15)) + 
  theme(legend.position="none"))
 
bothSitesTurb_simp # Print plot

### save plot with specified parameters directly to a specific file path
ggsave(file = "fig/bothSitesTurb_simp.svg", plot = bothSitesTurb_simp, width = 8, height = 6)

ggsave(file = "fig/bothSitesTurb_simp.pdf", plot = bothSitesTurb_simp, width = 8, height = 6)


# Plot 24-running average TDS over raw
(bothSitesTDS_simp <- ggplot(data = ysiSumm, aes(x = DT, color = site, fill = site)) +
  geom_ribbon(aes(ymin = TDSMin, ymax = TDSMax, alpha = 0.5), color = NA)+
  geom_line(aes (y = maTDS_24, color = site), size = 1) + 
  scale_color_manual(values=siteColorsLine) + # Manually change colors of plotted data
  scale_fill_manual(values=siteColorsPoint) + # Manually change colors of plotted data
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom") + 
  labs(color = "") +
  labs(x = "\nDate", # \n makes space above and below
       y = "TDS") +
scale_y_continuous(expand = c(0,0),   # # Sets the 0 of the y-axis to start at the plot outline and not have it floating above the plot
    limits = c(34000,37000))+  # Sets the y-axis to range from 0 to 10, based on the site with the widest range
 #   breaks = seq(0,10,1)) +  # Defines breaks in a sequence from 27.5 to 33 by increments of 1
  scale_x_datetime(breaks = as.POSIXct(c("2019-07-01", "2019-08-01", "2019-09-01", "2019-10-01")),
                   labels = c( "1-Jul", "1-Aug", "1-Sep", "1-Oct")) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15)) + 
  theme(text=element_text(size=15)) + 
  theme(legend.position="none"))
 
bothSitesTDS_simp # Print plot

### save plot with specified parameters directly to a specific file path
ggsave(file = "fig/bothSitesTDS_simp.svg", plot = bothSitesTDS_simp, width = 8, height = 6)

ggsave(file = "fig/bothSitesTDS_simp.pdf", plot = bothSitesTDS_simp, width = 8, height = 6)

# Plot 24-running average pH over raw
(bothSitespH_simp <- ggplot(data = ysiSumm, aes(x = DT, color = site, fill = site)) +
  geom_ribbon(aes(ymin = pHmin, ymax = pHmax, alpha = 0.5), color = NA)+
  geom_line(aes (y = mapH_24, color = site), size = 1) + 
  scale_color_manual(values=siteColorsLine) + # Manually change colors of plotted data
  scale_fill_manual(values=siteColorsPoint) + # Manually change colors of plotted data
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom") + 
  labs(color = "") +
  labs(x = "\nDate", # \n makes space above and below
       y = "pH") +
scale_y_continuous(expand = c(0,0),   # # Sets the 0 of the y-axis to start at the plot outline and not have it floating above the plot
    limits = c(7.9,8.4))+  # Sets the y-axis to range from 0 to 10, based on the site with the widest range
 #   breaks = seq(0,10,1)) +  # Defines breaks in a sequence from 27.5 to 33 by increments of 1
  scale_x_datetime(breaks = as.POSIXct(c("2019-07-01", "2019-08-01", "2019-09-01", "2019-10-01")),
                   labels = c( "1-Jul", "1-Aug", "1-Sep", "1-Oct")) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15)) + 
  theme(text=element_text(size=15)) + 
  theme(legend.position="none"))
 
bothSitespH_simp # Print plot

### save plot with specified parameters directly to a specific file path
ggsave(file = "fig/bothSitespH_simp.svg", plot = bothSitespH_simp, width = 8, height = 6)

ggsave(file = "fig/bothSitespH_simp.pdf", plot = bothSitespH_simp, width = 8, height = 6)


# Plot 24-running average Salinity over raw
(bothSitesSal_simp <- ggplot(data = ysiSumm, aes(x = DT, color = site, fill = site)) +
  geom_ribbon(aes(ymin = Sal_PSUmin, ymax = Sal_PSUmax, alpha = 0.5), color = NA)+
  geom_line(aes (y = maSal_24, color = site), size = 1) + 
  scale_color_manual(values=siteColorsLine) + # Manually change colors of plotted data
  scale_fill_manual(values=siteColorsPoint) + # Manually change colors of plotted data
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom") + 
  labs(color = "") +
  labs(x = "\nDate", # \n makes space above and below
       y = "Salinity (psu)") +
scale_y_continuous(expand = c(0,0),   # # Sets the 0 of the y-axis to start at the plot outline and not have it floating above the plot
    limits = c(34,38))+  # Sets the y-axis to range from 0 to 10, based on the site with the widest range
 #   breaks = seq(0,10,1)) +  # Defines breaks in a sequence from 27.5 to 33 by increments of 1
  scale_x_datetime(breaks = as.POSIXct(c("2019-07-01", "2019-08-01", "2019-09-01", "2019-10-01")),
                   labels = c( "1-Jul", "1-Aug", "1-Sep", "1-Oct")) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15)) + 
  theme(text=element_text(size=15)) + 
  theme(legend.position="none"))
 
bothSitesSal_simp # Print plot

### save plot with specified parameters directly to a specific file path
ggsave(file = "fig/bothSitesSal_simp.svg", plot = bothSitesSal_simp, width = 8, height = 6)

ggsave(file = "fig/bothSitesSal_simp.pdf", plot = bothSitesSal_simp, width = 8, height = 6)
```

